---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{r data_setup, include=FALSE}
library(tidyverse)
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vT-XuDDKN_RMNNYir_sx35rbufm1-8IiEYe7GsvPAjkQUIWD2Ku-gCCYEHHZ67ZGJh0ly7-vPG4FmSS/pub?output=csv")
latest_data <- logged_data %>%
  rename(date = 1,
         spending_amount = 2,
         category = 3)
table_date <- (table(latest_data$date))

table_category <- (table(latest_data$category))

```

```{css echo=FALSE}
<style>
body {
  font-family: Arial, sans-serif;
  margin: 20px;
  font-size: 20px
}
h2 {
  font-family: 'Arial', serif;
  font-weight: bold;
  font-size: 25px
}
</style>
```
# Analysis of Daily Spending Patterns

These graphs aim to analyse spending patterns and behaviour over the course of a week.

```{r fig.width = 12, fig.height = 4}
ggplot(data = latest_data, aes(x = date, y = spending_amount)) +
  geom_bar(stat = "identity", fill = "#109585") +
  scale_x_discrete(limits = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday")) +
  labs(title = expression(bold("Spending Amount over a Week")),
       x = expression(bold("Day of Week")),
       y = expression(bold("Spending Amount")))

ggplot(data = latest_data, aes(x = category, y = spending_amount, fill = category)) +
  geom_bar(stat = "identity") +
  labs(title = expression(bold("Spending Amount by Category")),
     x = expression(bold("Category of Spending")),
     y = expression(bold("Spending Amount")))
```

The mean amount of spending per day is `r round(sum(latest_data$spending_amount/7), 2)` dollars.

The total sum of spending in the week is `r round(sum(latest_data$spending_amount), 2)` dollars.

```{r fig.width =12, fig.height =4}
ggplot(data = latest_data) +
  geom_bar(aes(x = date,
               fill = category)) +
  labs(title = expression(bold("Instances of Spending by Category")))
             

ggplot(data = latest_data) +
  geom_bar(aes(x = category,
               fill = date)) +
  labs(title = expression(bold("Instances of Spending by Date")))
```

The most common category(s) for spending is `r names(table_category)[table_category == max(table_category)]`, 
and the day(s) with the most transactions is `r names(table_date)[table_date == max(table_date)]`.


